### 2020-08-20 5_Thesis/THESIS_LaTeX/Chapters/4.tex
file re organisation

\chapter{Fabrication of Polymeric Fibers through Near-Field Electrospinning, Photopolymerization and Pyrolysis of Polymeric Fibers} % Main chapter title

>>>>

\chapter{Fabrication of Polymeric Fibers through Near-Field Electrospinning, and Forward-thinking on Photopolymerization and Pyrolysis} % Main chapter title

### 2020-08-20 5_Thesis/THESIS_LaTeX/main.tex
file re organisation

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Fabrication of Graphitic-Carbon Suspended Nanowires Through Mechano-Near-Field Electrospinning of Photocrosslinkable Polymers}

@@

\textbf{CEM} & \textbf{C}ampus \textbf{E}stado de \textbf{M}éxico\\

\textbf{CNWs} & \textbf{C}arbon \textbf{N}ano-\textbf{w}ire\textbf{s}\\

\textbf{DC} & \textbf{D}irect \textbf{C}urrent\\

\textbf{EMS} & \textbf{E}lectro\textbf{m}echanical \textbf{S}pinning\\

\textbf{FFES} & \textbf{F}ar \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\

\textbf{ITESM} & \textbf{I}nstituto \textbf{T}ecnonólogico y de \textbf{E}studios \textbf{S}uperiores de \textbf{M}onterrey\\

\textbf{MA} & \textbf{Ma}ssachusetts\\

\textbf{MEMS} & \textbf{M}icro\textbf{e}lectro\textbf{m}echanical \textbf{S}ystems\\

\textbf{MNT} & \textbf{M}aestría en \textbf{N}ano\textbf{t}ecnología \emph{(Master of Science in Nanotechnology)}\\

\textbf{MTY} & \textbf{M}on\textbf{t}erre\textbf{y} \emph{or} Campus \textbf{M}on\textbf{t}erre\textbf{y}\\

\textbf{NFES} & \textbf{N}ear \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\

\textbf{USA} & \textbf{U}nited \textbf{S}tates of \textbf{A}merica\\

\textbf{UV} & \textbf{U}ltra\textbf{v}iolet\\

@@

%$a$ & distance & \si{\meter} \\
%$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
Symbol & Name & Unit \\

\addlinespace % Gap to separate the Roman symbols from the Greek

$\omega$ & angular frequency & \si{\radian} \\

>>>>

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Fabrication of Suspended Nanowires Through Mechano-Near-Field Electrospinning of Polymers in Solution for the Production of Glass-like Carbon}

@@

\textbf{CEM}   & \textbf{C}ampus \textbf{E}stado de \textbf{M}éxico\\
\textbf{CNWs}  & \textbf{C}arbon \textbf{N}ano-\textbf{w}ire\textbf{s}\\
\textbf{DC}    & \textbf{D}irect \textbf{C}urrent\\
\textbf{EMS}   & \textbf{E}lectro\textbf{m}echanical \textbf{S}pinning\\
\textbf{FFES}  & \textbf{F}ar \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\
\textbf{ITESM} & \textbf{I}nstituto \textbf{T}ecnonólogico y de \textbf{E}studios \textbf{S}uperiores de \textbf{M}onterrey\\
\textbf{MA}    & \textbf{Ma}ssachusetts\\
\textbf{MEMS}  & \textbf{M}icro\textbf{e}lectro\textbf{m}echanical \textbf{S}ystems\\
\textbf{MNT}   & \textbf{M}aestría en \textbf{N}ano\textbf{t}ecnología \emph{(Master of Science in Nanotechnology)}\\
\textbf{MTY}   & \textbf{M}on\textbf{t}erre\textbf{y} \emph{or} Campus \textbf{M}on\textbf{t}erre\textbf{y}\\
\textbf{NFES}  & \textbf{N}ear \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\
\textbf{USA}   & \textbf{U}nited \textbf{S}tates of \textbf{A}merica\\
\textbf{UV}    & \textbf{U}ltra\textbf{v}iolet\\

@@

%$a$ & distance & \si{\meter} \\
%$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
Symbol   & Name              & Unit \\
\addlinespace % Gap to separate the Roman symbols from the Greek
$\omega$ & angular frequency & \si{\radian} \\

### 2020-08-20 5_Thesis/thesis_proposal_LaTeX/Chapters/5_StateoftheArt.tex
file re organisation

@@

Flores studied SU-8 2002 polymer solutions in cyclopentanone with poly(ethylene) oxide (PEO) and tetrabutylammonium tetrafluoroborate (TBATFB). For that purpose, several samples were prepared with the adequate amounts of PEO and TBATFB with 5 $m l$ of SU-8 2002 and stirred at 160 $r p m$ for one hour at 75 $^\circ C$ in the absence of light. A 5 $m l$ syringe was used to extract the solution from the preparation vial. Finally the syringe was placed upside down for 24 hours to get rid of any bubbles within the solution. Table \ref{tbl:FloresSamples} lists the set of samples that were prepared as values in $w t \%$, dissolved in SU-8 2002.

\begin{table}[th]
\caption{Set of prepared samples}
\begin{center}
\begin{tabular}{ c c c c c c c } 
\hline
\text{} & \multicolumn{2}{c}{Serie A} & \multicolumn{2}{c}{Serie B} & \multicolumn{2}{c}{Serie C} \\
\hline
Sample & PEO & TBATFB & PEO & TBATFB & PEO & TBATFB \\
\hline
1 & 0.00 & 0.00 & 0.00 & 0.50 & 0.50 & 0.00 \\
2 & 0.25 & 0.25 & 0.25 & 0.50 & 0.50 & 0.25 \\
3 & 0.50 & 0.50 & 0.50 & 0.50 & 0.50 & 0.50 \\
4 & 0.75 & 0.75 & 0.75 & 0.50 & 0.50 & 0.75 \\
5 & 1.00 & 1.00 & 1.00 & 0.50 & 0.50 & 1.00 \\
\hline
\label{tbl:FloresSamples}
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieAampSweep.png}
\decoRule
\caption[Serie A - Amplitude Sweep]{Serie A - Amplitude Sweep}
\label{fig:SerieAampSweep}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieBampSweep.png}
\decoRule
\caption[Serie B - Amplitude Sweep]{Serie B - Amplitude Sweep}
\label{fig:SerieBampSweep}
\end{figure}

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieCampSweep.png}
\decoRule
\caption[Serie C - Amplitude Sweep]{Serie C - Amplitude Sweep}
\label{fig:SerieCampSweep}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieAflowCurve.png}
\decoRule
\caption[Serie A - Flow curve]{Serie A - Flow curve}
\label{fig:SerieAflowCurve}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieBflowCurve.png}
\decoRule
\caption[Serie B - Flow curve]{Serie B - Flow curve}
\label{fig:SerieBflowCurve}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieCflowCurve.png}
\decoRule
\caption[Serie C - Flow curve]{Serie C - Flow curve}
\label{fig:SerieCflowCurve}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieAfreqSweep.png}
\decoRule
\caption[Serie A - Frequency Sweep]{Serie A - Frequency Sweep}
\label{fig:SerieAfreqSweep}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieBfreqSweep.png}
\decoRule
\caption[Serie B - Frequency Sweep]{Serie B - Frequency Sweep}
\label{fig:SerieBfreqSweep}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieCfreqSweep.png}
\decoRule
\caption[Serie C - Frequency Sweep]{Serie C - Frequency Sweep}
\label{fig:SerieCfreqSweep}
\end{figure}

@@

The production of carbon structures involves to main procedures: a) polymer patterning such as photolithography, electrospinning, Computer Numerical Control (CNC), molding, hot embossing, and recently, Multiple Photon Polymerization; and b) carbonization, which induces further thinning of the patterned polymer and its conversion into carbon. Cardenas conducted some experiments to characterize and analyze carbon nano-wires. Polymeric SU-8 nano fibers were produced by two different methods; for each method different polymer solutions were employed.

@@

\subsubsection{Polymer Solution}
The polymeric solution was composed by 2 $ml$ of SU-8 2002 mixed with 0.5 $w t \%$ of PEO and 0.5 $w t \%$ of TBATFB to increase its conductivity and yield soother polymer jets during electrospinning. Magnetic stirring was performed for 1 $hr$ at 75 \textdegree{}$C$ with $rpm$ values between 100 and 150.

\subsubsection{Deposition}
A voltage around 100 $V$ was applied between a dispensing needle and the collector stage. The needle to collector distance was set to 100 $\mu m$. The collector was attached to a mechanically motorized stage, which allowed the SU-8 nanofibers patterning into the SU-8 microstructures. Three different stage velocities were tested (20,40 and 60 $mm/s$) to study the influence on the wire geometry. Acceleration of the stage was set to 500 $mm/s^{2}$. After deposition, samples were exposed to UV light for 45 $min$ to complete cross-linking.

@@

\subsubsection{Polymer Solution}
The solution was composed of 4 $ml$ of SU-8 2025, 4 $mg$ of TBATFB and 80 $\mu L$ of SU-8 thinner. The solution was stirred for 1.5 $hrs$ at 100 $rpm$ at 75 \textdegree{}$C$.

\subsubsection{Deposition}
To pattern the fiber exactly on top of the SU-8 electrodes, a routine was set to move the needle relative to the collector. The polymer solution was dispensed at a rate of 8.847 $nL / min$ using a programmable syringe pump. A voltage of 200 $V$ was applied between the collector plate and the needle tip, and the polymer solution was allowed to flow for between 15 to 30 $min$ until it was stable. A higher voltage had to be applied compared to Method 1 due to the higher viscosity of the SU-8 2025 solution. Once a steady flow was achieved, the collector was moved relative to the needle tip using the motorized stage. The mechanical parameters used during were: a) velocity of 5000 $\mu m/s$, an acceleration of 2500 $\mu m/s^{2}$. The sample was exposed to UV light for 45 min to ensure complete cross-linking of the deposited SU-8 nanofiber.

@@

Cardenas \cite{Cardenas2017} states that the geometry of the carbon nano-wires is also an important characteristic that affects the carbon structure conductivity, mechanical and thermal characteristics and crystallinity. The conducted experiments showed some techniques and materials that have been applied to fabricate carbon nano-wires, as well as the effects that fabrication parameters have on the final geometry of the carbon structures. The newly technique of electro-mechano-spinning (EMS) involved new polymer solutions along with a systematic deposition process. Cardenas found that the EMS proposed manufacturing technique yielded normally distributed diameters of 204 $nm$ with low variability, which is significantly reduced the uncertainty in the fabrication of carbon nano-wires.

\section{FIND PAPER THAT CONFIRMS THAT WITH THE INCREASE OF PEO CONCENTRATION, THE POROSITY DENSITY INCREASES IN CARBON STRUCTURES AFTER PYROLYSIS. \cite{newPAPER}}

As explained in Section \ref{sec:pyrolysis}, the pyrolysis process is implemented to thermally decompose organic material into carbon. ...

>>>>

The following is a literature review to highlight the work done by others that is related to the proposed dissertation. This section presents the work that the proposal is based on to show others attempts to solve a problem related to Section \ref{Chapter:ProblemDefinitionandMotivation}.

@@

\label{sec:FloresWrk}

\subsection{Rheometry}
Rheometry is the measuring technology used to determine rheological data. There are different measuring systems, instruments and analysis methods. Both, liquids and solid  can be investigated using rotational and oscillatory rheometers. Rotational tests are performed to characterize viscous behavior. In order to evaluate viscoelastic behavior, creep tests, relaxation tests and oscillatory tests are performed \cite{Flores2017}.

\subsubsection{Amplitude Sweep}
An amplitude sweep is a typical test used to characterize the behavior of a polymer
solution or polymer melt. In this basic test a constant angular frequency is applied along with an increasing or decreasing deformation or strain, see Figure \ref{fig:ampSweep} a). The obtained results are the storage and loss moduli, $G'$ and $G''$ respectively, along the values of percentage of strain applied. The amplitude is the maximum of the oscillatory motion. Normally at low frequencies the viscoelastic material presents a linear behavior, this is when the viscoelastic properties are independent of the strain or stress imposed due to the structure of the material stays undisturbed. Nevertheless, as the amplitude is increased at some at some point this linear trend changes suddenly. Once this critical amplitude value is reached the material becomes more elastic or viscous depending on the solution initial state, see Figure \ref{fig:ampSweep} b) \cite{Flores2017}.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/ampSweep.png}
\decoRule
\caption[Amplitude Sweep]{a) Imposed amplitude along time with constant frequency. b) Results for an amplitude sweep \cite{Flores2017}}
\label{fig:ampSweep}
\end{figure}

\subsubsection{Frequency Sweep}
A frequency sweep, is a common oscillatory test useful to understand the rheological behavior of fluids as it measures the viscoelastic properties. This measurement is considered a viscoelastic spectrum, in general, the shorter the timescale the more elastic the material behaves. These results are related to the molecular structure of the sample. Figure \ref{fig:freqSweep} shows a typical data for a polymer melt where different regions are observed. Frequency sweep measurements also allow the estimation of the molecular weight distribution characteristics such as entanglement density and process-ability \cite{Flores2017}.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/freqSweep.png}
\decoRule
\caption[Frequency Sweep]{Typical results for a frequency sweep. \cite{Flores2017}}
\label{fig:freqSweep}
\end{figure}

\subsubsection{Flow Curve}
The viscosity is measured as a function of the shear rate in a rotational rheometer with different geometries according to the sample. Normally three types of behaviours can be characterized in flow curve measurements: a) ideal viscous, b) shear thinning and c) shear thickening. Figure \ref{fig:flowCurve} shows three different materials and their response to an imposed shear rate \cite{Flores2017}.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/flowCurve.png}
\decoRule
\caption[Flow Curves]{a) Flow curve stress vs stress. b) Flow curve strain vs shear viscosity. Both figures for i Newtonian fluid, ii Shear thinning fluid, iii Shear thickening fluid. \cite{Flores2017}}
\label{fig:flowCurve}
\end{figure}

\subsection{Sample Preparation}
Flores studied SU-8 2002 polymer solutions in cyclopentanone with poly(ethylene) oxide (PEO) and tetrabutylammonium tetrafluoroborate (TBATFB). For that purpose, several samples were prepared with the adequate amounts of PEO and TBATFB with 5 $m l$ of SU-8 2002 and stirred at 160 $r p m$ for one hour at 75 $^\circ C$ in the absence of light. A 5 $m l$ syringe was used to extract the solution from the preparation vial. Finally the syringe was placed upside down for 24 hours to get rid of any bubbles within the solution. Table \ref{tbl:FloresSamples} lists the set of samples that were prepared as values in $w t \%$, dissolved in SU-8 2002.

\begin{table}[th]
\caption{Set of prepared samples \cite{Flores2017}}
\begin{center}
\begin{tabular}{ c c c c c c c } 
\hline
\text{} & \multicolumn{2}{c}{Serie A} & \multicolumn{2}{c}{Serie B} & \multicolumn{2}{c}{Serie C} \\
\hline
Sample & PEO & TBATFB & PEO & TBATFB & PEO & TBATFB \\
\hline
1 & 0.00 & 0.00 & 0.00 & 0.50 & 0.50 & 0.00 \\
2 & 0.25 & 0.25 & 0.25 & 0.50 & 0.50 & 0.25 \\
3 & 0.50 & 0.50 & 0.50 & 0.50 & 0.50 & 0.50 \\
4 & 0.75 & 0.75 & 0.75 & 0.50 & 0.50 & 0.75 \\
5 & 1.00 & 1.00 & 1.00 & 0.50 & 0.50 & 1.00 \\
\hline
\label{tbl:FloresSamples}
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieAampSweep.png}
\decoRule
\caption[Serie A - Amplitude Sweep]{Serie A - Amplitude Sweep \cite{Flores2017}}
\label{fig:SerieAampSweep}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieBampSweep.png}
\decoRule
\caption[Serie B - Amplitude Sweep]{Serie B - Amplitude Sweep \cite{Flores2017}}
\label{fig:SerieBampSweep}
\end{figure}

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieCampSweep.png}
\decoRule
\caption[Serie C - Amplitude Sweep]{Serie C - Amplitude Sweep \cite{Flores2017}}
\label{fig:SerieCampSweep}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieAflowCurve.png}
\decoRule
\caption[Serie A - Flow curve]{Serie A - Flow curve \cite{Flores2017}}
\label{fig:SerieAflowCurve}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieBflowCurve.png}
\decoRule
\caption[Serie B - Flow curve]{Serie B - Flow curve \cite{Flores2017}}
\label{fig:SerieBflowCurve}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieCflowCurve.png}
\decoRule
\caption[Serie C - Flow curve]{Serie C - Flow curve \cite{Flores2017}}
\label{fig:SerieCflowCurve}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieAfreqSweep.png}
\decoRule
\caption[Serie A - Frequency Sweep]{Serie A - Frequency Sweep \cite{Flores2017}}
\label{fig:SerieAfreqSweep}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieBfreqSweep.png}
\decoRule
\caption[Serie B - Frequency Sweep]{Serie B - Frequency Sweep \cite{Flores2017}}
\label{fig:SerieBfreqSweep}
\end{figure}

@@

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieCfreqSweep.png}
\decoRule
\caption[Serie C - Frequency Sweep]{Serie C - Frequency Sweep \cite{Flores2017}}
\label{fig:SerieCfreqSweep}
\end{figure}

@@

The production of carbon structures involves to main procedures: a) polymer patterning such as photolithography, electrospinning, Computer Numerical Control (CNC), molding, hot embossing, and recently, Multiple Photon Polymerization; and b) carbonization, which induces further thinning of the patterned polymer and its conversion into carbon. Cardenas conducted some experiments to characterize and analyze carbon nano-wires. Polymeric SU-8 nano fibers were produced by two different methods; for each method different polymer solutions were employed, See Table \ref{tbl:CardenasSummary}.

\begin{table}[th]
\caption{Method 1 and Method 2 conditions and parameters \cite{Cardenas2017}}
\begin{center}
\begin{tabular}{ >{\raggedright\arraybackslash}p{0.30\textwidth} >{\raggedright\arraybackslash}p{0.30\textwidth} >{\raggedright\arraybackslash}p{0.30\textwidth} } 
\hline
Conditions and Parameters & Method 1 & Method 2 \\
\hline
Solution materials & SU-8 2002, PEO and TBATFB & SU-8 2025, TBATFB and SU-8 thinner \\
Solution preparation & stirred for 1 $hr$ at 75$^\circ C$ at 100-150 $r p m$ & stirred for 1.5 $hrs$ at 75$^\circ C$ at 100 $r p m$ \\
Deposition voltage & 100 $V$ & 200 $V$ (due to the higher viscosity) \\
Results & failed the pyrolyzation process & 81\% yield rate after pyrolyzation \\
Fiber diameter & NA & 204 $nm$ \\
\hline
\label{tbl:CardenasSummary}
\end{tabular}
\end{center}
\end{table}

@@

\subsubsection{SU-8 2002 Polymer Solution}
The polymeric solution was composed by 2 $ml$ of SU-8 2002 mixed with 0.5 $w t \%$ of PEO and 0.5 $w t \%$ of TBATFB to increase its conductivity and yield soother polymer jets during electrospinning. Magnetic stirring was performed for 1 $hr$ at 75 \textdegree{}$C$ with $rpm$ values between 100 and 150.

\subsubsection{Deposition of Electrospun SU-8 2002 Solution}
A voltage around 100 $V$ was applied between a dispensing needle and the collector stage. The needle to collector distance was set to 100 $\mu m$. The collector was attached to a mechanically motorized stage, which allowed the SU-8 nanofibers patterning into the SU-8 microstructures. Three different stage velocities were tested (20,40 and 60 $mm/s$) to study the influence on the wire geometry. Acceleration of the stage was set to 500 $mm/s^{2}$. After deposition, samples were exposed to UV light for 45 $min$ to complete cross-linking.

@@

\subsubsection{SU-8 2025 Polymer Solution}
The solution was composed of 4 $ml$ of SU-8 2025, 4 $mg$ of TBATFB and 80 $\mu L$ of SU-8 thinner. The solution was stirred for 1.5 $hrs$ at 100 $rpm$ at 75 \textdegree{}$C$.

\subsubsection{Deposition of Electrospun SU-8 2025 Solution}
To pattern the fiber exactly on top of the SU-8 electrodes, a routine was set to move the needle relative to the collector. The polymer solution was dispensed at a rate of 8.847 $nL / min$ using a programmable syringe pump. A voltage of 200 $V$ was applied between the collector plate and the needle tip, and the polymer solution was allowed to flow for between 15 to 30 $min$ until it was stable. A higher voltage had to be applied compared to Method 1 due to the higher viscosity of the SU-8 2025 solution. Once a steady flow was achieved, the collector was moved relative to the needle tip using the motorized stage. The mechanical parameters used during were: a) velocity of 5000 $\mu m/s$, an acceleration of 2500 $\mu m/s^{2}$. The sample was exposed to UV light for 45 min to ensure complete cross-linking of the deposited SU-8 nanofiber.

@@

Cardenas \cite{Cardenas2017} states that the geometry of the carbon nano-wires is also an important characteristic that affects the carbon structure conductivity, mechanical and thermal characteristics and crystallinity. The conducted experiments showed some techniques and materials that have been applied to fabricate carbon nano-wires, as well as the effects that fabrication parameters have on the final geometry of the carbon structures. The new technique of electro-mechano-spinning (EMS) involved new polymer solutions along with a systematic deposition process. Cardenas \cite{Cardenas2017} found that the EMS proposed manufacturing technique yielded normally distributed diameters of 204 $nm$ with low variability, which is significantly reduced the uncertainty in the fabrication of carbon nano-wires.

%\clearpage
%
%\section{FIND PAPER THAT CONFIRMS THAT WITH THE INCREASE OF PEO CONCENTRATION, THE POROSITY DENSITY INCREASES IN CARBON STRUCTURES AFTER PYROLYSIS. \cite{newPAPER}}
%
%As explained in Section \ref{sec:pyrolysis}, the pyrolysis process is implemented to thermally decompose organic material into carbon. ...
